Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
figs
Minor modification on abstract.

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In this article, we present a tool
  to efficiently explore the curvature tensor on the boundary of
  potentially large digital objects. More precisely, we combine a
  fully parallel pipeline on GPU to extract an adaptive triangulated
  isosurface of the digital object, with a curvature tensor
  estimation at each surface point based on integral
  invariants. Integral invariants being parametrized by a given ball
  radius, our proposal allows us to explore interactively different
  radii and thus select the appropriate scale to which the computation
  is performed and visualized (mean and gaussian curvature, principal
  curvatures, principal directions and normal vector field).

@@

Once decisions have been made, a new set of cells are sent to the mesh
generation step described above. Updating the cell buffer can be
efficiently implemented on GPU hardware as illustrated in
Figure~\ref{fig_lod_octree}-\emph{rigth}.

>>>>

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In this article, we present a tool
  to efficiently explore the curvature tensor on the boundary of
  potentially large digital objects. More precisely, we combine a
  fully parallel pipeline on GPU to extract an adaptive triangulated
  isosurface of the digital object, with a curvature tensor
  estimation at each surface point based on integral
  invariants. Integral invariants being parametrized by a given ball
  radius, our proposal allows us to explore interactively different
  radii and thus select the appropriate scale to which the computation
  is performed and visualized. Mean and gaussian curvature, principal
  curvatures, principal directions and normal vector field may be interactively
  visualized with our technique.

@@

Once decisions have been made, a new set of cells are sent to the mesh
generation step described above. Updating the cell buffer can be
efficiently implemented on GPU hardware as illustrated in
Figure~\ref{fig_lod_octree}-\emph{right}.
